Invariant Representations for Noisy Speech Recognition

### 2016-11-30 poster.tex
Improve introduction

\begin{block}{Introduction}
    \begin{itemize}
        \item 
    Modern automatic speech recognition (ASR) systems need to be robust under 
    acoustic variability arising from environmental, speaker, channel, and recording 
    conditions. Ensuring such robustness to variability is a challenge in modern day 
    neural network-based ASR systems, especially when all types of variability are 
    not seen during training.

        \item We attempt to address this problem by encouraging the 
    neural network acoustic model to learn invariant feature representations.

        \item We use ideas from recent research on image generation using
    Generative Adversarial Networks and domain adaptation ideas extending
    adversarial gradient-based training. A recent work from Ganin et al. proposes to
    use adversarial training for image domain adaptation by using an intermediate
    representation from the main target classification network to deteriorate the 
    domain 
    classifier performance through a separate neural network.
    Our work focuses on investigating neural architectures which produce
    representations invariant to noise conditions for ASR.  
        \item We evaluate the proposed 
    architecture on the Aurora-4 task, a popular benchmark for
    noise robust ASR. We show that our method generalizes better than the standard 
    multi-condition training especially when only a few noise categories are seen 
    during training.
    \end{itemize}

@@

        \item The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``fake'' generated image and the ``real'' image taken from the dataset~\cite{goodfellow2014generative}. 
    \begin{align*}
        \min_G \max_D V(D, G) = & \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
            & \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}

@@

    \begin{block}{Domain Adaptation with Reverse Gradient}
        \begin{itemize}
            \item 
            Prior work by~\cite{ganin2014unsupervised} proposed a method of training a network 
            which can be adapted to new domains.

            \item $Y$-like network: the image is fed to the
            encoder network ($E$) which produces a hidden representation $h$.

>>>>

\begin{block}{Introduction}
    \begin{itemize}
        \item 
            \textcolor{dblue}{Robustness} to the acoustic variability arising from environmental, speaker, channel, 
    and recording 
    conditions is a challenge in modern day 
    neural network-based ASR systems, especially when all types of variability are 
    not seen during training.

        \item We attempt to address this problem by encouraging the 
            neural network acoustic model to learn \textcolor{dblue}{invariant} feature representations.

        \item We use ideas from recent research on image generation using
            \textcolor{dblue}{generative adversarial networks} and domain adaptation ideas extending
    adversarial gradient-based training.  
        \item We evaluate the proposed 
    architecture on the Aurora-4 task, a popular benchmark for
    noise robust ASR. 
    \end{itemize}

@@

        \item The discriminator network $D$
    can either receive a generated image from the generator $G$ or an image
    from the training set. Its task is to distinguish
    between the ``fake'' generated image and the ``real'' image taken from the dataset~\cite{goodfellow2014generative}:
    \begin{align*}
        \min_G \max_D V(D, G) = & \mathbb{E}_{\bm{x} \sim p_{\text{data}}(\bm{x})}[\log D(\bm{x})] + \\
            & \mathbb{E}_{\bm{z} \sim p_{\bm{z}}(\bm{z})}[\log (1 - D(G(\bm{z})))].
    \end{align*}

@@

    \begin{block}{Domain Adaptation with Reverse Gradient}
        \begin{itemize}
            \item \cite{ganin2014unsupervised} proposes $Y$-shaped network: the image is fed to the
            encoder network ($E$) which produces a hidden representation $h$.
